Adolescent well-being in the digital age

### 2022-04-08 00-clean.Rmd
Combine predictors to one table

-   Create lagged and centered predictors
-   Transform edge values of internet variable to fit beta
    -   2 values were changed (0 in Timor-Leste in 2002, and 1 in UAE 2020)
-   Join outcome and predictor tables
-   Center year on 2010 (roughly in the middle)
-   Ensure that age and sex are treated with contrast codes

```{r model-prepare-data}
# Create lagged predictors
itu <- itu %>% 
  arrange(region, country, year) %>%
  group_by(region, country) %>%
  mutate(
    across(
      c(internet, mobile),
      list(`1` = ~ lag(., 1)),
      .names = "{str_sub(.col, 1, 1)}{.fn}"
    )
  ) %>% 
  ungroup()

# Centering predictors within and between countries
itu <- itu %>%
  group_by(country) %>%
  mutate(
    i1_cb = mean(i1, na.rm = TRUE), # Country average
    i1_cw = i1 - i1_cb, # Year-specific deviation from country average
    m1_cb = mean(m1, na.rm = TRUE),
    m1_cw = m1 - m1_cb,
  ) %>%
  # Grand-mean center the country averages
  ungroup() %>% 
  mutate(
    across(c(i1_cb, m1_cb), ~ . - mean(., na.rm = T))
  )

@@

```{r}
write_rds(dat, "data/data-all.rds")
write_rds(itu, "data/itu.rds")
write_rds(gwp, "data/gwp.rds")
write_rds(gbd, "data/gbd.rds")
write_rds(hdi, "data/hdi.rds")
```

>>>>

-   Combine all predictors into one table (primary ITU and controls HDI)
-   Create lagged and centered predictors
-   Transform edge values of internet variable to fit beta
    -   2 values were changed (0 in Timor-Leste in 2002, and 1 in UAE 2020)
-   Join outcome and predictor tables
-   Center year on 2010 (roughly in the middle)
-   Ensure that age and sex are treated with contrast codes

```{r model-prepare-data}
# Merge different predictors to itu
itu <- left_join(itu, hdi)

# Create lagged predictors
itu <- itu %>% 
  arrange(region, country, year) %>%
  group_by(region, country) %>%
  mutate(
    across(
      c(internet, mobile, hdi),
      list(`1` = ~ lag(., 1)),
      .names = "{str_sub(.col, 1, 1)}{.fn}"
    )
  ) %>% 
  ungroup()

# Centering predictors within and between countries
itu <- itu %>%
  group_by(country) %>%
  mutate(
    # Year-specific deviations from country average
    i1_cw = i1 - mean(i1, na.rm = TRUE), 
    m1_cw = m1 - mean(m1, na.rm = TRUE),
    h1_cw = h1 - mean(h1, na.rm = TRUE)
  ) %>% 
  ungroup()

@@

```{r}
write_rds(dat, "data/data-all.rds")
write_rds(itu, "data/itu.rds")
write_rds(gwp, "data/gwp.rds")
write_rds(gbd, "data/gbd.rds")
```
